%---------------------------------------------------
% Nombre: bibliografia.tex  
% 
% Bibliografia
%---------------------------------------------------

\begin{thebibliography}{99}

\bibitem{github}
	\emph{} Repositorio del proyecto. \url{https://github.com/joseangeldiazg/}

\bibitem{kaggle}
	\emph{} Website de Kaggle \url{https://www.kaggle.com}	

\bibitem{challenge}
	\emph{} Competicion en Kaggle. \url{https://www.kaggle.com/c/intel-mobileodt-cervical-cancer-screening}
	
\bibitem{tutorial1}
	\emph{} Tutorial MXNET. \url{https://www.kaggle.com/miguelpm/r-mxnet-simple-tutorial}
	
\bibitem{tutorial2}
	\emph{} Script Tensorflow. \url{https://www.kaggle.com/marek3000/test-num-001/code}
	
\bibitem{tutorial3}
	\emph{} Tutorial uso red pre-entrenada \url{https://github.com/dmlc/mxnet/blob/master/R-package/vignettes/classifyRealImageWithPretrainedModel.Rmd}
	
\bibitem{resnet50}
	\emph{}Kaiming He, Xiangyu Zhang, Shaoqing Ren, Jian Sun. Deep Residual Learning for Image Recognition.
	
\bibitem{mc3}
	\emph{} Mikel Galar, Alberto Fernández, Edurne Barrenechea, Humberto Bustince, Francisco Herrera, An overview of ensemble methods for binary classifiers in multi-class problems: Experimental study on one-vs-one and one-vs-all schemes, Pattern Recognition, Volume 44, Issue 8, 2011, Pages 1761-1776, ISSN 0031-3203.
	
\bibitem{mc1}
	\emph{} \url{http://www.tamps.cinvestav.mx/~wgomez/diapositivas/RP/Clase11.pdf}

\bibitem{mc2}
	\emph{} \url{http://www.aepia.org/aepia/files/EVIA/TransparenciasEVIA2016/Sanz_Galar_Fernandez_EVIA2016.pdf}
	
\bibitem{auc}
	\emph{} Desarrollo de un módulo de evaluación probabilística. \url{http://joseangeldiazg.github.io/tfg_roc_keel/}	
	
	
\bibitem{ensembles}
	\emph{} Jianjun Liu Shengping Xia Weidong Hu Wenxian Yu. Weights Updated Voting for Ensemble of Neural Networks Based Incremental Learning. International Symposium on Neural Networks. Advances in Neural Networks ? ISNN 2009 pp 661-669
	
	
\end{thebibliography}
%---------------------------------------------------